Leadership across cultures and contexts: an exploratory analysis

### 2020-04-26 leadership_across_cultures_contexts.Rmd
Added model of high status by subsistence and region. Tweaked cost benefit plot

```{r leadertotalbenefitscosts, fig.cap="Estimated marginal means of A. leader total benefits, and B. total costs, as a function of group structure, based on a Poisson mixed effects regression model with random intercepts for ethnographer nested within culture. Values are on the response scale."}
p1 <- 
  hagenutils::ggemmeans(emmeans(m_ldrtotben, type = 'response', specs = 'group.structure2')) +
  labs(title = "Total leader benefits", x = "", y = "")

p2 <- hagenutils::ggemmeans(emmeans(m_ldrtotcost, type = 'response', specs = 'group.structure2')) +
  labs(title = "Total leader costs", x = "\nRate", y = "")

@@

>>>>

```{r leadertotalbenefitscosts, fig.cap="Estimated marginal means of A. leader total benefits, and B. total costs, as a function of group structure, based on a logistic mixed effects regression model with random intercepts for ethnographer nested within culture. Values are on the response scale."}
p1 <- 
  hagenutils::ggemmeans(emmeans(m_ldrtotben, type = 'response', specs = 'group.structure2')) +
  scale_x_continuous(limits = c(0, 0.1)) +
  labs(title = "Total leader benefits", x = "", y = "")

p2 <- hagenutils::ggemmeans(emmeans(m_ldrtotcost, type = 'response', specs = 'group.structure2')) +
  scale_x_continuous(limits = c(0, 0.1)) +
  labs(title = "Total leader costs", x = "\nProbability", y = "")

@@

Finally, we examined the relationship between evidence for high status and subsistence strategy and continental region. See Figure \@ref(fig:statusregion).

```{r statusregion, fig.cap="Estimated marginal means of a mixed effects logistic regression model of evidence for high status (0/1) as a function of subsistence strategy and region as covariates, with random effects for ethnographer nested within culture."}
plot_status_subsistence + plot_status_region + plot_layout(ncol = 1)
```
